---
title: "Advanced: Visualization"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced: Visualization}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(vanda)
library(ggplot2)
```

## Visualizing V&A Data

This vignette demonstrates how to visualize search results to understand trends in the collection.

```{r get-data}
client <- mcp_connect()
# Search for a broad term to get diverse data
data <- mcp_search(client, "Chair")
```

## Plotting Popularity over Time

We can visualize how the popularity of items varies by their creation date and genre.

```{r plot, fig.width=7, fig.height=5}
vanda_visualise(data, x_col = "date", y_col = "popularity", color_col = "genre")
```

## Faceting by Period

We can use standard `ggplot2` functions to further customize the plot, for example, faceting by period.

```{r facet, fig.width=7, fig.height=5}
vanda_visualise(data, x_col = "date", y_col = "popularity", color_col = "artist") +
  facet_wrap(~period)
```

## Session Info

```{r session-info}
sessionInfo()
```